\TITLE

### 2023-01-30 paper/ieee.tex
split the tex into subtexs

\documentclass{ieeeaccess}

\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}

\usepackage{caption}
\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{scalerel}

@@

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2022.0122113}

\title{Privacy-preserving physical delivery service provisioning using distributed networks}
\author{\uppercase{Stanis\l{}aw Bara{\'n}ski} \authorrefmark{1},
\uppercase{Julian Szyma{\'n}ski\authorrefmark{1} } 
 }

@@

\markboth{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Privacy-preserving physical delivery service provisioning using distributed networks}
{S. Bara{\'n}ski, J. Szyma{\'n}ski : 
Privacy-preserving physical delivery service provisioning using distributed networks}

@@

\begin{abstract}
Service providers like lawyers, laboratories, auditors, or banks, to provide services, require customers to submit data often associated with their personal information, exposing their customers to privacy risks. However, most service providers use personal information merely for logistic operations like payments and communication and could provide services anonymously if other means of logistics exist.
We propose a anonymous fair exchange protocol for coordinating service provision using blockchain for both anonymous payments and proofs of existence and content-addressable network for results delivery.
% Less important
A service provider can employ our protocol to provide services without collecting personal information, enabling services currently based on unacceptable trust assumptions. 
% Even less important
Possible applications for this protocol include anonymous tests for drugs, venereal diseases, paternity, and steroids, or anonymous legal advice.
We provide the fairness analysis and well as the implementation of the protocol. We discuss further extensions to an anonymous delivery system, and a decentralized conflict resolution system.
\end{abstract}

\begin{keywords}
Anonymity, blockchain, fair-exchange, physical delivery, privacy, services
\end{keywords}

@@

\section{Introduction}
\label{sec:introduction}
Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.

Providing personal information exposes users to privacy risks, i.e. potential loss of control over personal information~\cite{smithInformationPrivacyResearch2011}.

Such personal information can be used deliberately or unintentionally
(e.g., by theft) for insider disclosure, unauthorized access, or commercial gains. For example, by reselling it to marketers, financial institutions, other businesses, government agencies, or even cybercriminals. Which in turn can lead to profiled advertisements or criminal activities like identity theft or illegal tracking and surveillance~\cite{smithInformationPrivacyResearch2011}.

Important individuals like influencers, politicians, or celebrities are especially vulnerable to this kind of attack as exposure of their health records, purchase habits, or legal documents can threaten their reputation, position or be used for blackmailing.

The privacy guarantee of the personal information is often based merely on trust assumptions and the security of the IT system. However, most SPs do not need personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

It would be desirable for the user to keep its identity private while still receiving the service. This could lead to reduced trust that users have to put on SPs and less responsibility borne by SPs.

Examples of services that would benefit from the anonymity property are:
\begin{itemize}
    \item Patients willing to take a test for drugs, venereal diseases, paternity or steroids have a strong incentive to keep the whole procedure private. Merely the fact that they took the test—without exposing the result—is suggestive enough to act as a premise in case of a conflict.

Especially celebrities, politicians, and public figures are prone to this kind of problem as such precedent can negatively influence their future career.

Currently, they have to risk that their personal details, materials, and results are stored securely and kept in private from any unauthorized actor (both curious employee and malicious attacker).

Our protocol allows taking such tests anonymously, eliminating the strong trust assumption put on the laboratories and their IT
systems.
\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

By exposing our identity we trust that the lawer will not use that information for harmful actions.

Our protocol would allow taking such advice anonymously, eliminating the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

% We observe
We observe that the issue of anonymous service provision can be seen as a problem of fair exchange where parties exchange some goods fairly, i.e., either both parties obtain the goods, or they both obtain nothing.

In our case, the customer who wants to use the service, exchanges his materials and money with the SP for the result of the service.

% Therefore we propose
We propose a protocol for anonymously provisioning services that require the delivery of physical materials. A service provider employing our protocol can provide services without collecting any personal information from customers.

In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehaviour of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allowing customers to pay for the services anonymously.
    \item Content-addressable decentralised storage network (e.g., IPFS) to anonymously provide results to customers together with provable storage netwrok (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP deny of service. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

\end{itemize}

%\paragraph{Contributions}
We contribute to the state of the art by:

\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in advantageous position, and customer in disadvantageus with the option to start a dispute in case the SP misbehaviour.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analysing fairness analysis in fair-exchange protocols.
\item Discuss the possible improvements to the protocol witht the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
\end{itemize}

% Our protocol simultaneously provides five main properties:

% \begin{itemize}
% \item Anonymity: the customer stays anonymous to all external observers throughout the transaction.
% \item Fairness: at each step of the protocol, both parties are incentivized to act accordingly to the protocol; otherwise, the misbehaving party ends up in a disadvantaged position.
% \item Dispute resolution: at each step of the protocol, the customer can start a dispute and win the case if and only if the SP misbehaved.
% \item Blockchain-obvious: the customer using our protocol does not need to interact with the blockchain directly; especially, he does not need to obtain funds and pay for the transaction fees, allowing the use of our protocol for non-technical users.
% \item TTP-less: 
% our protocol does not rely on a trusted third party to conduct transactions fairly. Only in case of a dispute, the centralised justice is involved, which can be instantiated either with courts and polices, or blockchain-based dispute resolution mechanisms as discussed in Section~\ref{sec:decentralised-justice}.
% \item Physical materials: our protocol allows providing not only digital but also physical materials to the service provider.
% \end{itemize}

Some authors have proposed blockchain-based fair-exchange systems that could be adapted to service provision; however, to our best knowledge, we are the first to propose a system that satisfies all the properties stated above. Especially anonymity and physical materials delivery were rarely addressed together, and if so, the protocol was based on TTP and impractical assumptions on banking system~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} or did not address the conflict between parties~\cite{altawyLelantosBlockchainBasedAnonymous2017}.

%\paragraph{Organisation}
The remainder of this paper is organized as follows.
In section~\ref{sec:related-works} we review related works. 
Then, in section~\ref{sec:building-blocks} we discuss the building blocks of dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), and anonymous delivery.
Finally, section~\ref{sec:conclusion} concludes the paper.

\section{Related Works}\label{sec:related-works}
In this section we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.

\subsection{Fair exchange, anonymity, and physical products delivery} 
\label{anonymity-and-fair-exchange-in-e-commerce-protocol-for-physical-products-delivery}

The most common application of anonymous fair exchange protocols is e-commerce. The problem is that the customer wants to buy a product from a merchant, but does not want to reveal his identity to the merchant. The problem gets even more challenging when physical products are involved.

Authors of~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} proposed a protocol for fair exchange of physical products and electronic payments, which guarantee both customer and merchant anonymity. They achieve it by introducing online TTPs that validate coins and provide fair exchange guarantees.

The anonymity is ensured by assuming the existence of a source cabinet (SC), delivery cabinet (DC), and a trusted delivery agent who take a product from a SC and provide it to a DC.
Both cabinets provide access to the product by passwords to conceal
the identity of the customer and the merchant.

The protocol works as follows: \begingroup
\renewcommand{\labelenumii}{\arabic{enumii}.}

\begin{enumerate}
    \item Both parties agree on the purchase details.
    \item The customer buys a digital coin from his bank and validates it with the TTP.
    \item The customer sends the merchant the purchase order and the digital signature made by TTP on the encrypted coin.
    \item The merchant post the product to the SC.
    \item Delivery agent collects the product from the SC and posts it to the DC.
    \item Customer collects the product from the DC using a password.
    \item The customer checks if the product is the ordered one.
    \begin{itemize}
    \item[-] if yes 
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the customer sends the acknowledge to the DC and decryption key to the merchant.
        \item The merchant redeem the coins from the bank.
        \end{enumerate}
    \item[-] if no
        \begin{enumerate}
        \setcounter{enumii}{7}
        \item the DC is equipped with a video camera that records the moment when the customer opens the package and lets the customer signal the invalidity of the product, and so, sending the encrypted recording to the TTP. 
        \item the dispute is settled via TTP, optionally letting each party reveal its identity.
    \end{enumerate}
    \end{itemize}
\end{enumerate}
\endgroup

However, the protocol relies on strong assumptions, namely:

\begin{itemize}
    \item there exists trusted third party (TTP) and trusted delivery agent which do not misbehave or collude with any party;
    \item there exists an anonymous communication channel 
    \item the customer's and merchant's banks enable confidential transactions, and both share commit-buffer where the value is locked until the transaction is finished;
    \item all banks maintain a global list of coins' serial numbers to prevent double-spending problems;
    \item the SC and DC exist, and in both, the access is protected by a password;
    \item the DC is equipped with a video camera that records the moment when the customer opens the package and provides a way to submit the video to TTP in case of a dispute;
\end{itemize}

\subsection{Fair exchange and blockchain}

The issue of TTPs in fair exchange protocols has been solved by the usage of decentralised networks, especially blockchain technology.

The simplest example of blockchain-based fair exchange protocol is certified electronic mail protocol in which neither the sender can deny sending the mail, nor the receiver can deny receiving it. As the service is widely used in the paper world, achieving it for e-mails has not yet met the agreement across the scientific community. The main problem was the dependency of TTP, which significantly reduced the performance, security, and robustness of such protocols. The protocols that do not use TTP struggle with high computation and communication overhead~\cite{hinarejosSolutionSecureCertified2019}.

Authors of ~\cite{hinarejosSolutionSecureCertified2019} replaced the TTP with blockchain (concretely Bitcoin blockchain as a reference implementation) that acts as a secure, verifiable, and decentralized TTP.

The idea behind certified e-mails and any other fair exchange protocols is following:
\begin{enumerate}
    \item The sender sends encrypted and signed message to the receiver.
    \item The receiver returns a proof of delivery (a signature) of the encrypted message to the sender.
    \item The sender publishes proof of delivery and the decryption key on a blockchain (or TTP in general).
    \item The receiver decrypts the encrypted message using the published decryption key.
\end{enumerate}

The non-repudiation requirement is achieved by the receiver sending the proof of delivery prior to having access to the decrypted message and the sender publishing the decryption key together with the proof of delivery on the blockchain (or TTP) so that the receiver can deny neither receiving the message nor having access to the decryption key—because it is publicly available.

In this case, the role of blockchain is to certify the existence of the decryption key at a certain time.

\subsection{Fair-exchange, blockchain, and decentralized dispute resolution}
\label{themis-towards-decentralized-escrow-of-cryptocurrencies-without-trusted-third-parties}

Themis~\cite{mengThemisDecentralizedEscrow2019} is a fair exchange protocol that uses blockchain instead of TTP. It provides an escrow service for the secure exchange of cryptocurrencies and digital goods. Also, it provides a decentralized dispute resolution system for resolving conflicts.

Two parties say, Alice and Bob, can create an escrow by generating
2-of-2 (not 2-of-3 as it is other TTP-based systems) threshold account
using Thresh-Key-Gen protocol. Alice and Bob generate secret keys
\(x_A\) and \(x_B\) accordingly, the shared account public key becomes
\(y = g^{x_A+x_B}\); only the access to both Alice's and Bob's secrets
grants access to the shared account.

Then, both Alice and Bob take their keys and split them into
\(n=2t+1\) secret shares using Shamir Secret Shamir protocol, where
\(n\) is the number of mediators that participate in the decentralized
network and \(t+1\) becomes the threshold of a sufficient number of mediators to reconstruct the secret key.

Next, both Alice and Bob, take their key shares, and encrypt each
\textit{i}-th key share using public key of \textit{i}-th mediator. As a result
Alice's secret \(x_A\) becomes \({c^A_1, c^A_2,...,c^A_n}\), and Bob's
secret \(x_B\) becomes \({c^B_1, c^B_2,...,c^B_n}\), where
\(c_i = E_{M_i}(P_i)\) is the encrypted \(i\)-th key share using
\(i\)-th mediator public key \(M_i\).

Next, both Alice and Bob exchange the sets of encrypted key shares with
each other, and send funds to the escrow account.

The escrow is secure as long as \(t+1\) of mediators does not collude,
which would let them recreate both \(x_A\) and \(x_B\). To ensure
that parties exchange actual key shares, they send witnesses
generated with the Feldman VSS scheme and zero-knowledge proofs to guarantee the consistency between witnesses and key shares.

In case of dispute, the decentralized network of mediators settle the conflict and grand one winning party, the other party secret key,
letting him withdraw the funds.

The monetary incentivization and reputation system guarantee the honesty of mediators.

\subsection{Blockchain, anonymity, and physical delivery}\label{lelantos-a-blockchain-based-anonymous-physical-delivery-system}

Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based anonymous
physical delivery system. The protocol achieves anonymity by employing onion routing (similar to the Tor network) to connect physical delivery providers. The whole route from a merchant to a customer is split into multiple steps, and each step is undertaken by the different randomly selected delivery providers. As long as the delivery providers do not collude, a merchant neither can learn the identity nor destination address of the customer.

Onchain smart-contract is used to coordinate the whole process and
mediate communication between customers and delivery providers.

However, since the system uses Ethereum, it achieves pseudonymity rather than anonymity (see section~\ref{sec:pseudo-anon}). Also, the protocol does not cover disputes between the parties.

\subsection{Comparision}

We considered only protocols that achieve fair exchange as it is the fundamental feature of such protocols.

Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} is the closest to our protocol, however it uses TTP and does not consider dispute between parties.

Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} is the simplest protocol that replaces TTP with blockchain. However, it does not consider anonymity, dispute between parties nor physical material exchange.

Meng et al., 2019~\cite{mengThemisDecentralizedEscrow2019} improves the previous protocol by the crownsource dispute resolution system. However it does not take anonimity into consideration.

Altawy et al., 2017~\cite{altawyLelantosBlockchainBasedAnonymous2017} is a blockchain-based protocol that does not provide dispute resolution, but provides anonymous physical delivery by using onion routing and anonymous blockchain interaction assuming unlinkability between pseudonyms and real identities.

Our protocol achieves stronger anonymity guarantees. Namely, we achieve anonimity by using either cash or privacy-preserving blockchains. Moreover, our protocol does not require a customer to submit any transaction to the message board, which may be the weakest link in the anonymity of aforementioned protocols.

Our protocol does not use its own delivery system. We assume that there is a way to anonymously deliver a package either via SP's drop box, or trusted party.

Also, our protocol does not provide its own dispute resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. It can be instantiated with either local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, 2019, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

The comparision of the protocols is presented in table~\ref{tab:comparision}.

\begin{table}
  \newcommand{\YES}{\cellcolor{green!50}Yes}
  \newcommand{\ID}{\cellcolor{green!25}Identity}
  \newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
  \newcommand{\ANON}{\cellcolor{green!50}Anonymity}
  \newcommand{\NO}{\cellcolor{red!50}No}
  \newcommand{\TTP}{\cellcolor{red!50}TTP}
  \newcommand{\BC}{\cellcolor{green!50}BC}
  \caption{Related work comparision}
  \label{tab:comparision}
  \setlength{\tabcolsep}{3pt}
  \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
  \hline
  Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
  \hline
  Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
  \hline
  Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
  \hline
  Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
  \hline
  Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
  \hline
  This paper & \YES & \YES & \YES & \BC & \YES \\
  \hline

  \end{tabular}
\end{table}

\section{Building Blocks}\label{sec:building-blocks}
\subsection{Dispute resolution system}

Disputes are an inevitable part of all human transactions. Whether intentional or accidental, the system should prevent violation of agreed contract rules or local jurisdiction. The rules are specified by law and implemented by the police.

The vision of smart contracts was to replace the legal contract with
programmable and autonomous contracts. The smart contract code encompasses the contract's specifications, hence the slogan \textit{code as a law}. Moreover, smart contracts are automatically executed merging together the gap of law and its enforcment by police~\cite{allenGovernanceBlockchainDispute2019}. However, the blockchain paradigm has its limitations.

Blockchain can assure the correctness of data existing only on the blockchain. The problem arises in the contact between blockchain and the real world, when we want the smart contract to decide based on some input from outside the blockchain. The technique of providing real-world data to the blockchain is called oracle. Oracle provides data based on a decentralized network of mediators; therefore, the trust is also decentralized~\cite{breidenbachChainlinkNextSteps2021}.

Some oracles provide the data like weather, soccer match result, stock
price, train delay, election results, others—and they are the ones we
are interested in—provide the settlement of a submitted dispute.

Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
resolve disputes by a set of voluntary anonymous mediators participating
in voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

Kleros~\cite{bergollaKlerosSociolegalCase2022} is a smart contract deployed on the Ethereum platform that mimics in a decentralized and autonomous way how the court works in real life. In Kleros, every process of a dispute like gathering evidence, selecting jurors, rewarding the winning party is automated by a set of smart contracts. Like Themis, the honesty of the agents voting in a case is achieved by game-theoretical economic incentives.

Such a decentralized, voluntary, and anonymous dispute resolution system might work for simple contracts violations like an eBay seller sending broken or wrong products or an Airbnb apartment being inadequate to the photos in the offer. However, it is hard to realize such decentralized evaluation of heath or legal services quality when expertise and privacy concerns are taken into account. Therefore, in our protocol, we take the more conservative approach and resolve disputes using local
justice system (police or court).

Possible directions toward semi-autonomous decentralized resolution system are discussed in Section~\ref{sec:decentralised-justice}.

\subsection{Fairness}\label{fairness}

In case of dispute, the customer can prove to justice (police or court) convincing evidence for the honesty of the customer and misbehaviour of the SP. 
Because the customer is anonymous, the SP can not start a dispute---there is no means to identify the customer.

To mitigate the issue, we designed the protocol so that the SP who follows the protocol is always in an advantaged position; therefore, she has no reason to start a dispute. On the other hand, the customer can start a dispute at any time of the protocol, but only the actual misbehaviour of the SP makes him win the case.

Abstracting from the services the SP is providing, each party should be able to prove its honest behaviour in case of a dispute. We introduce three proofs that should be disclosed to justice in case of a dispute:

\begin{enumerate}
    \item Proof of delivery ($\mathrm{PoD}$) is a confirmation issued by the SP to the customer that proves that the customer has delivered to the SP a complete (according to the SP requirements) package, and the SP accepted it. It consists of the current time, the deadline to pay for the transaction, the deadline to provide a result of the service, randomly generated number uniquely identifying the transaction, and the SP's signature guaranteeing non-repudiation. The formal definition of the $\mathrm{PoD}$ is presented in section ~\ref{proof-of-delivery}.

    \item Payment $\mathrm{attestation}$ is confirmation that the customer has paid for the transaction at a certain time. The actual implementation depends on the particular cryptocurrency and is discussed further section~\ref{payment-for-services}.

    \item Proof of provision ($\mathrm{PoP}$) is proof that the SP published the result at a certain time. It defends the SP in case the customer unjustly starts a dispute after the result has been published. It consists of a content identifier as specified in section ~\ref{storage-network}, the $\mathrm{nonce}$ uniquely identifying the transaction previously generated in $\mathrm{PoD}$, and the SP's signature guaranteeing authentication. The connection between $\mathrm{PoP}$ and the result is created by the content identifier ($\mathrm{cid}$) that uniquely identify the result (it is some kind of a hash of the result) such that the result can not be forged after the $\mathrm{PoP}$ has been published.
\end{enumerate}

\subsection{Message Board}\label{sec:message-board}
The proof of provision that we coined for the purpose of this protocol is generally called the proof of existence~\cite{ProofExistenceOnline, crespoStamperyBlockchainTimestamping2017, ChainpointBlockchainProof}.

The idea behind proof of existence is to certify that some information
has existed at a certain moment, in such a way that nobody can
undermine its existence, integrity, and ownership (also called the
non-repudiation requirement).

We need this functionality for two reasons: (1) communicate the existence of the result to the customer to whom the SP have no other communication medium as the customer stays anonymous; (2) let the SP to proof the publication of the result within the agreed with customer deadline.

By publishing the $\mathrm{PoP}$ on the blockchain, the SP can not falsify the time at which the result has been provided because the block creation time proves that. Blockchain acts as a global clock that securely timestamps everything that gets into the block, so the $\mathrm{PoP}$ that was included in a block will be associated with the time when the block has been created. Moreover, since the blockchain is public, everyone (including justice) can be convinced that the SP indeed published the result at that time.

Without such proof, there would be no other means to settle the conflict between the customer claiming the result has not been published and the SP claiming the result has been published within the deadline.

Depending on the context the platform of achieving it is called bulletin board~\cite{achenbachImprovedCoercionresistantElectronic2015}, trusted timestamping~\cite{gippDecentralizedTrustedTimestamping2015}, or message board~\cite{hinarejosSolutionSecureCertified2019}. In this work, we call it a message board.

We keep the protocol general enough to be implemented using any existing technology to provide message board service, assuming it is decentralized and supports subscribing for the upcoming proofs from a particular address.

\subsection{Anonymity, pseudonomity, and confidentality}\label{sec:pseudo-anon}

Privacy is a concept used in almost all social sciences like philosophy, psychology, sociology, and legal. The multidisciplinary nature leads to ambiguous definitions~\cite{smithInformationPrivacyResearch2011}. For our work, we rely on more concrete definitions, i.e.~confidentality and anonymity.

Confidentiality is the ability to hide the details of an action from others. Alternatively, we can say that the system guarantees confidentiality if, for all observers, everything they can say about the action is the fact that it happened and nothing more.

Anonymity is the ability to hide one identity from others. More precisely, the inability to correlate actions performed within the system with the user's identity. Alternatively, we can say that the system guarantees anonymity if, for all observers, the actions are equally likely to be associated with any user of the system. However, anonymity is a spectrum rather than a dichotomous classification. One method of quantifying the level of anonymity is \textit{k}-anonymity proposed in~\cite{sweeneyKanonymityModelProtecting2002}. It measures the user's anonymity by the number of other users from whom the user can not be distinguished. Concretely, the user is \textit{k}-anonymous if his actions are equally likely associated with \textit{k}-1 other users; the larger \textit{k}, the higher anonymity.

Some anonymity techniques can be deployed on non-anonymous blockchains. The so-called mixers gather users into an \textit{anonymity set}, which then collude together to launder transactions in such a way that to an observer, the likelihood of the sender of each transaction is equiprobable for any user from the anonymity set.

Some systems guarantee pseudonymity rather than anonymity. Pseudonymity allows users to hide their real identity behind the pseudonyms. Despite the whole system being transparent and allowing linking actions to pseudonyms, the system is considered anonymous as long as the link between pseudonyms and real identities is secret. This assumption is hard to satisfy in practice, as the KYC (Know Your Customer) and AML (Anti Money Laundering) regulations require users to reveal their real identity to cryptocurrencies exchanges, making the user's anonymity dependent on the security of the IT system. Moreover, some correlations can be inferred merely by the analysis of transactions \cite{androulakiEvaluatingUserPrivacy2013, oberStructureAnonymityBitcoin2013}.

The figure ~\ref{fig:anonymity-diagram} ilustrate relations between these terms.

\begin{figure}[h!]
\includegraphics[width=9cm]{anonymity-diagram.png}
\centering
\caption{Let us assume Alice to be the customer willing to keep her identity anonymous and Bob to be the public SP. Alice controls two addresses, 1 and 2; the connection between her real identity and the first address has been compromised, and therefore the identification is possible; the connection between the second pseudonym is still unknown therefore anonymous. Alice takes two actions; the first one from the compromised address and the second one from the anonymous one. The first action is confidential; therefore, even though the pseudonym has been compromised, the action can not be associated with Alice. The second action is transparent; therefore, Alice maintain her anonymity as long as the connection to the second pseudonym is concealed.}

\label{fig:anonymity-diagram}
\end{figure}

The privacy-preserving blockchains are the ones that maintain anonymity via untraceability and (ideally) unlikability, not via the assumption that the connection between an address (pseudonym) and the real identity is concealed.

Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{moneroBulletproofsMoneropediaMonero, bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{Wasabi Wallet, Open-source, non-custodial Bitcoin Wallet for desktop, \url{https://wasabiwallet.io/}, (last visited Nov. 28, 2022)} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).

\subsection{Payment for services}\label{payment-for-services}
Transactions between customers and SPs must be pegged to prevent proving one payment for multiple transactions. In other
words, we need a mechanism that uniquely associates a payment with the corresponding transaction.

Depending on a cryptocurrency, the link can be created in different
ways:
% continue reading from here
\begin{itemize}

\item separate address: each transaction derives a new address uniquely associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals,Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec. 03, 2022)}.
\item memo: the payments are sent to one SP account but contain an extra field named ``memo'' filled with the unique number provided by the SP in $\mathrm{PoD}$. Each payment containing such value in the memo is considered to pay for the transaction. In case of a dispute, revealing both the payment memo and the $\mathrm{PoD}$ proves the connection.
\end{itemize}

Both approaches have some advantages and disadvantages, but our protocol can abstract them away by treating them as some randomly generated unique number, often called \textit{nonce} (number once). The actual implementation depends on a particular blockchain.

In case of a dispute, there must be a way to prove to the justice that the customer has paid for the transaction. As the proof of transaction is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains. Monero allows proving and checking payments via dedicated API \cite{MoneroHowProve}. ZCash provides a mechanism called Payment Disclosure \cite{daviesIntroductionPaymentDisclosure2017}.

\subsection{Storage network}\label{storage-network}
Once the SP finishes its service, she has to provide the result to the customer. The most natural approach would be to send the result via e-mail or some dedicated platform. However, since the customer wants to stay anonymous and so does not want to expose his e-mail address nor IP address. Moreover, the SP should prove that the result has been provided before the deadline, which brings us to the issue of proof of existence discussed in section ~\ref{sec:message-board}.

One approach would be to post the result into a blockchain. However, storing data on a blockchain is very expensive. The most common workaround (\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}) is to publish the data on a content addressable peer-to-peer storage network like IPFS~\cite{benetIPFSContentAddressed2014}. Then, publish on the blockchain just the content identifier ($\mathrm{cid}$) that uniquely points to the content stored on IPFS.

We take the same approach. Once the SP creates the result, she encrypts it using the previously provided encryption key and uploads it to the IPFS network.
%TODO: write about DHKE encyption

To increase anonymity, the customer should use standard techniques to hide its IP address, such as gateway, VPN, proxy, or onion routing.

\subsection{Separation of concerns}
We could use one blockchain to achieve all of these three roles: (i) anonymous payments, (ii) message board, (iii) storage network.

While most blockchains could provide the message board functionality, anonymous payments are not as prevalent. Especially a provable storage network is a functionality of a few specialized blockchains.

Instead of searching for one blockchain that provides all the functionalities, we allow the protocol to use separate blockchains for each role. If a suitable blockchain arises, it can play more than one role.

At the time of writing, we see the following technologies that fulfil the requirements of each role:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}

>>>>

\documentclass{ieeeaccess}
\usepackage{cite}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}

\usepackage{caption}
\usepackage{url}
\usepackage{listings}
\usepackage{pdfpages}
\usepackage[english]{babel}
\usepackage{xcolor,colortbl}
\usepackage{scalerel}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}

\input{constants.tex}

@@

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\history{Date of publication xxxx 00, 0000, date of current version xxxx 00, 0000.}
\doi{10.1109/ACCESS.2022.0122113}
\title{\TITLE}

\author{\uppercase{\STANLONG} \authorrefmark{1},
\uppercase{\JULLONG{}} \authorrefmark{1}}

@@

\markboth{\STAN{}, \JUL{} : \TITLE}
{\STAN{}, \JUL{} : \TITLE}

@@

\begin{abstract}
  \ABSTRACT{}
\end{abstract}

\newcommand{\sep}{,}
\begin{keywords}
Anonymity\sep{} blockchain\sep{} fair-exchange\sep{} physical delivery\sep{} privacy\sep{} services
\end{keywords}

@@

\def\JOURNALIEEE{IEEE}
\def\JOURNALELS{ELS}

\def\JOURNAL{\JOURNALIEEE}

\input{content}

\EOD

\bibliographystyle{IEEEtran}

% Loading bibliography database
\bibliography{bibliography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{stanislaw.jpg}}]{Stanis\L{}aw Bara{\'n}ski} received BEng in 2019 and MSc in 2020 in informatics at Gdańsk University of Technology. 
Currently, he is a PhD student at the Department of Computer Architecture, Faculty of Electronics, Telecommunications and Informatics, Gdansk University of Technology.
